Buildtime Trend : What's trending in your build process

### 2015-04-01 buildtimetrend/presentation.tex
remove unused macro
improve affiliation
add subtitle
improve text
add project description

% macro for double dash
\newcommand{\dd}{{\texttt{-{}-}}}

@@

@@

\institute[Buildtime Trend]{Buildtime Trend founder, developer - @dcadriaenssens}

@@

    %(question to audience : who knows/uses iptables?)

@@

@@

      \item Some builds took longer than others

@@

    One solution : bash + CSV + gnuplot\\

@@

    I hadn't used Python before.\\

>>>>

@@

\subtitle{What, why and how}

@@

\institute[]{Buildtime Trend founder \& developer - @dcadriaenssens}

@@

    Buildtime Trend is an Open Source application that uses (timing) data to visualise trends in a build process.

@@

    I was working on a project that was built on Travis CI:

@@

      \item some builds took longer than others

@@

    One solution : Bash + CSV + gnuplot\\

@@

    I didn't use Python before.\\
